---
title: "Meta-Analysis (TG-Trustor)"
author: "Liam A. Doyle"
date: "2024-07-05"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(meta)
library(metafor)
library(devtools)
library(esc)
library(effectsize)
library(psych)
library(dmetar)
library(readxl)
```

```{r import, include=FALSE}
TG_Trustor <- read_excel("C:/Users/lad81/Desktop/TG_Trustor/TG_Trustor.xlsx")
```

```{r recode, include=FALSE}
TG_Trustor$Sample_Source <- factor(TG_Trustor$Sample_Source,
                                  levels = c(0, 1, 2, 3),
                                  labels = c("Community", "Student", "Inmate", "Mixed"))

TG_Trustor$Publication_Status <- factor(TG_Trustor$Publication_Status,
                                       levels = c(0, 1),
                                       labels = c("Unpublished", "Published"))

TG_Trustor$Measure_coded <- factor(TG_Trustor$Measure_coded,
                                       levels = c(0, 1, 2, 3, 4, 5, 6),
                                       labels = c("SRP", "PCL", "PPI", 
                                                  "LSRP", "TriPM", "SD3",
                                                  "DD"))

TG_Trustor$Iterated <- factor(TG_Trustor$Iterated,
                                       levels = c(0, 1),
                                       labels = c("One-shot", "Iterated"))

TG_Trustor$Perceived_Opponent <- factor(TG_Trustor$Perceived_Opponent,
                                        levels = c(0, 1),
                                        labels = c("No", "Yes"))

TG_Trustor$Social_role <- factor(TG_Trustor$Social_role,
                                       levels = c(0, 1),
                                       labels = c("Close member", "Distant member"))

TG_Trustor$Incentives <- factor(TG_Trustor$Incentives,
                               levels = c(0, 1, 2),
                               labels = c("Not incentivized", "Participation incentivized",
                                          "Performance incentivized"))

TG_Trustor$Experimental_Manipulation <- factor(TG_Trustor$Experimental_Manipulation,
                                                levels = c(0, 1),
                                                labels = c("No Manipulation",
                                                           "Manipulation"))

TG_Trustor$Feedback <- factor(TG_Trustor$Feedback,
                                levels = c(0, 1),
                                labels = c("No feedback", "Feedback"))
```

```{r transform, include=FALSE}
TG_Trustor <- TG_Trustor %>%
  mutate(z_psyc_coop = 0.5 * log((1 + Psyc_Invest)/(1 - Psyc_Invest)))

TG_Trustor <- TG_Trustor %>%
  mutate(z_se_psyc_coop = 1/(sqrt(n_effect - 3)))

TG_Trustor <- TG_Trustor %>%
  mutate(var_z_psyc_coop = (z_se_psyc_coop^2))
```

## Project Description

This is an R Markdown file that documents for some of the analyses conducted for the first study in my dissertation. Specifically, this file documents the simple random effects meta-analytic model conducted for the effect of psychopathy on behaviour in the Trust Game as a Trustor (TG-Trustor).

## Simple Random Effects Model of Psychopathy on Cooperation in the TG-Trustor

```{r model, echo=FALSE, warning=FALSE}
TG_Trustor <- drop_na(TG_Trustor, Psyc_Invest)

psyc.coop <- metacor(cor = Psyc_Invest,
                     n = n_effect,
                     studlab = Study,
                     data = TG_Trustor,
                     fixed = FALSE,
                     random = TRUE,
                     method.tau = "REML",
                     method.random.ci = "HK",
                     title = "Psychopathy and Cooperation in the TG-Trustor")

summary(psyc.coop)
```

## Forest Plot of Psychopathy-Cooperation Meta-Analysis

```{r forest plot, echo=FALSE, warning=FALSE, fig.width=10, fig.height=7, out.width='250%', out.height='250%'}
forestplot <- meta::forest(psyc.coop,
                           sortvar = Psyc_Invest,
                           prediction = TRUE,
                           print.tau2 = TRUE)
```

## Drapery Plot of Psychopathy-Cooperation Meta-Analysis

```{r drapery plot, echo=FALSE, warning=FALSE}
drapery(psyc.coop,
        labels = "studlab",
        type = "pval",
        srt.labels = 45,
        legend = TRUE)
```

## Funnel Plot of Psychopathy-Cooperation Meta-Analysis

```{r funnel plot, echo=FALSE, warning=FALSE}
meta::funnel(psyc.coop,
             xlim = c(-1, 1),
             studlab = FALSE)

title("Funnel Plot of the Effect Sizes for the Psychopathy-Cooperation Relationship")
```

## Egger's Regression Test

```{r egger, echo=FALSE, warning=FALSE}
metabias(psyc.coop,
         method.bias = "linreg",
         k.min = 4)
```

## Fail-Safe *N*

```{r fail-safe, echo=FALSE, warning=FALSE}
fail.safe <- rma(yi = z_psyc_coop,
                 vi = var_z_psyc_coop,
                 slab = Study,
                 data = TG_Trustor,
                 random = ~ 1 | Study/Effect_size_ID,
                 test = "t",
                 method = "REML")

fsn(fail.safe, type = "General", target = 0.05)
```